%% Adonay Berhe							CS 383
%% November 1, 2016						Assignment 4
%\title{Overleaf Memo Template}
% Using the texMemo package by Rob Oakes
\documentclass[a4paper,12pt]{texMemo}
\usepackage[english]{babel}


\memoto{Professor Bruce Bolden}
\memofrom{Adonay Berhe}
\memosubject{First Design Spec}
\memodate{November 1, 2016}

\begin{document}
\maketitle
\section*{Introduction}
This memorandum is intended to explain the discussions and activities performed by the group and highlight the contributions that I made in the process. 

\section*{Overview}
\begin{itemize}
\item Team met and discussed major UI features to be included in the software.
\item Individual members presented the major issues observed.
\item Team members suggested critical and extended features.
\item Team discussed and prioritized features to fit \textbf{\textit{agile}} work flow. 
\item I was charged with writing the specifications of the Menu bar. 
\end{itemize}

\section*{Summary}
The assignment served as a great avenue to further acquaint myself with Latex and Git. I still had a few issues with GitHub, but it was, overall, a smooth process. Writing out the specifications for the Menu bar made me realize the interdependencies that exists among developers in a team and highlight the importance of communicating clearly and meeting deadlines. This project has already proven to showcase the various topics we have discussed class; I'm excited to progress to the next step. 
\bigskip
\newline UML and QT, here we come!

\end{document}