%Matthew Holman			11-1-2016
%cs383					Design Document Memo

% memo for submission of first draft of design spec
\documentclass[12pt]{article}
\begin{document}

{\noindent \hspace*{-0.3cm} \begin{tabular}{l l}
	\textbf{To:} & Bruce Bolden\\
	\textbf{From:} & Matthew Holman\\
	\textbf{Subject:} & Tower of Lights Design Document - First Version\\
	\textbf{Date:} & 11/1/2016 \\
\end{tabular}}

\vspace{0.5cm}
{\noindent \textbf{Introduction}\\\par
This is a brief summary of my efforts in contributing to the design document of my group's `Tower of Lights' project.\\\par}

{\noindent \textbf{Overview}\\\par
My group and I met at our normal time, 3:30 p.m., on Friday, October 28th 2016. The purpose of this meeting was to discuss design ideas for the project, and assign various parts of the design document to different team members to work on. Basically, we all took turns listing off all of the features that we thought could be in the project. Basically, there were three categories of features: the user interface, which included things like a tool box, menu bar, etc., the `core functionality' of the project, which included file handling, creating frames, etc., and finally the `additional features' portion, which included things like being able to clear a frame, saving custom colors, etc.\par
My main contributions to the meeting were in terms of the additional features. Among other things, since there is no interaction between the music and the visuals in the program, I suggested that the `playback' button not only play the light patterns, but play the music as well. My other main suggestion was to create a way to make a musical `score' of time values based on the tempo of the song, so that each `beat' of the song has a frame created at the appropriate time index. This would save quite a few clicks and enable the user to more accurately choreograph the lights to the song.\par}

{\noindent\textbf{Summary}\\\par
For the design document, I volunteered to write out the `additional features' portion of the document. I completed this portion of the document over the weekend (October 29th and 30th), and created a layout for the main document as well that all the different group member's contributions could be linked to.\par}  
\end{document}