% memo for submission of first draft of design spec
\documentclass[12pt]{article}
\begin{document}
	\noindent
	\textbf{To:} Bruce Bolden \newline
	\textbf{From:} Trevor Morse\newline
	\textbf{Subject:}  Rough Draft of Design Spec\newline
	\textbf{Date:} \today	\newline\newline
	
	\noindent\textbf{Introduction} \newline
	This memo outlines my thoughts regarding and contributions to the initial draft of my team's design specification.\\
	
	\noindent\textbf{Overview}\newline
	After receiving the assignment last Wednesday, I suggested that each member of our team compile a list of core functionality and possible improvements for the ToL program. In our regularly scheduled meeting that Friday, we listed all of these items on the whiteboard to see where our ideas overlapped. From there, we divvied up the design specification by section and organized the remaining work through Slack and GitHub.\\

	\noindent\textbf{Summary}\newline
	As with the rest of my teammates, I compiled a list of items that I viewed as core functionality for the program as well as a list of possible improvements, should time allow. I also proposed a new UI design at our Friday meeting that I thought might help simplify and organize the program layout. Overall, the team seemed to like the design, and a couple of them suggested some helpful improvements or additions.\\
	
	\noindent On Saturday, I messaged the team over Slack with a compilation of our notes and takeaways from the meeting. I also setup the directory within our Git repo for the design spec documents so that everyone could work with the same structure. After that, I handled the reviewing of my team members' sections, seeking to help us all maintain a consistent format and flow throughout the document. I also wrote my section covering the editor portion of the GUI. Finally, after everyone had completed their different sections and memos, I compiled all the work together into our spec document and made the necessary modifications for it to mesh.\\
	
	\noindent Overall, I would say we have a decent first draft of the spec. However, it will certainly change as we continue work, communication of plans and ideas, and understand the project better.

\end{document}
